%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
%\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
	\cvpub{\textbf{Milan Rybář}, Riccardo Poli, and Ian Daly. \href{https://doi.org/10.1038/s41597-025-04967-0}{\textbf{Simultaneous EEG and fNIRS recordings for semantic decoding of imagined animals and tools}}. 2025 Scientific Data.}
	
	\cvpub{\textbf{Milan Rybář}, Riccardo Poli, and Ian Daly. \href{https://doi.org/10.1038/s41598-024-79309-y}{\textbf{Using data from cue presentations results in grossly overestimating semantic BCI performance}}. 2024 Scientific Reports.}
	
	\cvpub{\textbf{Milan Rybář}. \href{https://repository.essex.ac.uk/34893/}{\textbf{Towards EEG/fNIRS-based semantic brain-computer interfacing}}. 2023 Doctoral dissertation, University of Essex.}
	
	\cvpub{\textbf{Milan Rybář} and Ian Daly. \href{http://dx.doi.org/10.1088/1741-2552/ac619a}{\textbf{Neural decoding of semantic concepts: a systematic literature review}}. 2022 Journal of Neural Engineering. }
	
	\cvpub{\textbf{Milan Rybář}, Riccardo Poli, and Ian Daly. \href{https://doi.org/10.1088/1741-2552/abf2e5}{\textbf{Decoding of semantic categories of imagined concepts of animals and tools in fNIRS}}. 2021 Journal of Neural Engineering.}
	
	\cvpub{\textbf{Milan Rybář}, Riccardo Poli, and Ian Daly. \href{https://doi.org/10.1109/EMBC44109.2020.9176314}{\textbf{Potential pitfalls of widely used implementations of common spatial patterns}}. 2020 42nd Annual International Conference of the IEEE Engineering in Medicine \& Biology Society (EMBC). \\
		\href{http://milanrybar.cz/data/EMBC2020/Potential pitfalls of widely used implementations of CSPs.pdf}{[PDF]},
		\href{https://youtu.be/f1wPn9G0tQw}{[Video Presentation]},
		\href{https://github.com/milan-rybar/csp_evaluation}{[Source codes at GitHub]}}

	\cvpub{Ian Daly and \textbf{Milan Rybář}. \href{https://doi.org/10.1109/embc44109.2020.9176690}{\textbf{Neural component analysis: source localisation for motor imagery classification}}. 2020 42nd Annual International Conference of the IEEE Engineering in Medicine \& Biology Society (EMBC).}

	\cvpub{\textbf{Milan Rybář} and Heiko Hamann. \href{http://dl.acm.org/citation.cfm?doid=2908812.2908815}{\textbf{Inspiration-Triggered Search: Towards Higher Complexities by Mimicking Creative Processes}}. In Proceedings of the Genetic and Evolutionary Computation Conference 2016 (GECCO '16).  \\
		\href{http://milanrybar.cz/inspiration-triggered-search}{[Info]}, 
		\href{http://milanrybar.cz/data/ITS/GECCO2016/ITS_GECCO2016_Paper.pdf}{[PDF]},
		\href{http://milanrybar.cz/data/ITS/GECCO2016/ITS_Supplementary_material_Full_quality.pdf}{[Example images with classification]}, 
		\href{https://github.com/milan-rybar/inspiration-triggered-search}{[Source codes at GitHub]}}

\end{cvpubs}


%% %---------------------------------------------------------
%\cvsubsection{In Review}
%% %---------------------------------------------------------
%
%\begin{cvpubs}
%	\cvpub{Manuscript 1}
%	
%	\cvpub{Manuscript 2}
%\end{cvpubs}
%
%% %---------------------------------------------------------
%\cvsubsection{In Prep}
%% %---------------------------------------------------------
%
%\begin{cvpubs}
%	\small \color{black}
%	\cvpub{Manuscript 1}
%	
%	\cvpub{Manuscript 2}
%\end{cvpubs}
%
%% %---------------------------------------------------------
